### 2013-07-02 cws/emnlp_cws/discussion.tex
writing additions etc

In this section we talked about detailed consistency analysis and maybe give some examples.
\subsection{Dual decomposition convergence}
Plot the histogram of the number of iterations it takes to converge, and percentage of optimality.

\subsection{consistency}

give results of the consistency analysis

\subsection{oracle}

Give results of the oracle experiment

\subsection{Error analysis}
Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.

>>>>

%In this section we talked about detailed consistency analysis and maybe give some examples.

\subsection{Dual decomposition convergence}
Plot the histogram of the number of iterations it takes to converge, and percentage of optimality.

\subsection{Consistency}

\cite{Chang:2008:ACL} have shown that increased segmentation consistency is correlated with better machine translation performance. Following their method for calculating the conditional entropy of a segmentation system, we see in Table [insert table] that our dual decomposition method achieves the most consistent results on 6 out of 7 datasets.

Consistency Results, Sighan 2003:

as crf
0.0428091404101
as pct
0.0441475626702
as dd
0.042168035925
cityu crf
0.0946373294134
cityu pct
0.10025983369
cityu dd
0.0867128300158
ctb crf
0.174004652166
ctb pct
0.18632727645
ctb dd
0.165767655651
pku crf
0.0423983535204
pku pct
0.0543269973345
pku dd
0.045000565176

Consistency Results, Sighan 2005:

as crf
0.0718479895225
as pct
0.0681887138263
as dd
0.0624082516494
cityu crf
0.0660880615807
cityu pct
0.0742624297
cityu dd
0.0627869624389
msr crf
0.0755273737469
msr pct
0.064051889613
msr dd
0.0558050161967
pku crf
0.0892311495453
pku pct
0.0998921318846
pku dd
0.0868198134889

\subsection{Oracle}

Following \cite{Sun:2010:COLING}, we run an oracle experiment to estimate the upper bound of improvement possible via system combination to further contextualize our results.

To do so, we combine our two baselines with the gold-standard segmentation. Each character in the test set is labeled with three \emph{B} or \emph{I} tags, \emph{B} when it begins a word and \emph{I} when it is word-medial or word-final, according to our two baselines and the gold standard. We then create oracle labels by majority vote: if the baselines agree, their label is used; if they disagree, the gold label is used.

The results of this oracle experiment, shown in Table [insert table], show that [what do they show? DD approaches the upper bound possible?]

% this is here to know what each column means in the output below
%=== TOTAL INSERTIONS:	75
%=== TOTAL DELETIONS:	84
%=== TOTAL SUBSTITUTIONS:	783
%=== TOTAL NCHANGE:	942
%=== TOTAL TRUE WORD COUNT:	11989
%=== TOTAL TEST WORD COUNT:	11980
%=== TOTAL TRUE WORDS RECALL:	0.928
%=== TOTAL TEST WORDS PRECISION:	0.928
%=== F MEASURE:	0.928
%=== OOV Rate:	0.022
%=== OOV Recall Rate:	0.810
%=== IV Recall Rate:	0.930
Scoring Oracle Output, Sighan 2003
for as
	sighan2003/as.oracle	75	84	783	942	11989	11980	0.928	0.928	0.928	0.022	0.810	0.930
for cityu
	sighan2003/cityu.oracle	402	333	2364	3099	35087	35156	0.923	0.921	0.922	0.071	0.824	0.931
for ctb
	sighan2003/ctb.oracle	920	1005	4490	6415	39921	39836	0.862	0.864	0.863	0.181	0.773	0.882
for pku
	sighan2003/pku.oracle	186	187	1593	1966	17194	17193	0.896	0.897	0.897	0.069	0.834	0.901

Scoring Oracle Output, Sighan 2003
for as
	sighan2005/as.oracle	1855	726	9980	12561	122610	123739	0.913	0.904	0.908	0.043	0.722	0.921
for cityu
	sighan2005/cityu.oracle	577	371	3038	3986	40936	41142	0.917	0.912	0.914	0.074	0.817	0.925
for msr // currently broken
	sighan2005/msr.oracle	81	107	1066	1254	10987	10961	0.893	0.895	0.894	0.025	0.584	0.901
for pku
	sighan2005/pku.oracle	800	1661	9646	12107	104372	103511	0.892	0.899	0.895	0.058	0.815	0.896

\subsection{Error analysis}
% this makes sense, i will do this tomorrow
Maybe look at cases where the model choose the worse of the two instead of the better of the two. See if there are patterns or insights we can draw. Not very important for a short paper.

### 2013-07-02 cws/emnlp_cws/experiment.tex
cleaned up results section, added a table to experiment section
writing additions etc

Give URL for the Stanford CRF segmenter. The perceptron-based word segmenter is a re-implementation of \cite{Zhang:2007:ACL}.
For development data, we used:
Training: CTB section 1-270  400-931 1001-115;   Dev: CTB section 271-300.

@@

>>>>

In this work, we employ two baseline models --- a character-based CRF and a word-based perceptron --- and test the performance of jointly decoding these baseline systems with dual decomposition. For our character-based CRF, we use the open-source Stanford CRF segmenter described in \cite{Tseng:2005:SIGHAN}.\footnote{http://nlp.stanford.edu/software/segmenter.shtml}
For our word-based perceptron, we use a reimplementation of \cite{Zhang:2007:ACL}.

% question: what is the relationship between this dev data and that used in sighan2003/2005?
For development data, we used:
Training: CTB section 1-270  400-931 1001-115;   Dev: CTB section 271-300.

@@

\begin{table}
\centering
\begin{small}
\begin{tabular}{ l | l | c | c | c | c | c   }
%\cline{2-10}
%\hline
% &   \multicolumn{1}{|c}{Models} & \multicolumn{1}{c}{$\lambda$} & \multicolumn{1}{c|}{No. of experts} & {P} & {R} & {F$_1$}   & \multicolumn{1}{c}{P} & \multicolumn{1}{c}{R} & \multicolumn{1}{c}{F$_1$}   \\
\hline
    \multicolumn{2}{c}{}  &  \multicolumn{1}{c}{\#W.T.} &  \multicolumn{1}{c}{\#W} &  \multicolumn{1}{c}{\#C.T.}    & \multicolumn{1}{c}{\#C}   &  \multicolumn{1}{c}{OOV}  \\ 
\hline
\multirow{4}{*}{2005}  & AS      & -  &  -  & -  &  - & 4.3   \\
& MS      & 88K & 2.3M & 5K & 4.1M & 2.6 \\
& PU      &  55k & 1.1M & 5K & 1.8M & 5.8  \\
& CU      & 69K  & 1.5M& 5K & 2.4M & 7.4 \\
\hline
\multirow{3}{*}{2003} & AS  &  - & - & - & - & 2.2 \\
& PU  &  - & - & - & - & 6.9 \\
& CU  & - & - & - & - & 7.1  \\
%\hline
%\multirow{4}{*}{CTB}  &  Best03  &  \textbf{0.886}  & 0.875 &  \textbf{0.881} & 0.181 & 0.644  & \textbf{0.927} \\
%& PcpTr       & 0.869 & 0.865 & 0.867 & 0.181 & 0.680  & 0.910 \\
%& PcpTr & 0.865 & 0.871 & 0.868 & 0.181 & 0.660 & 0.910 \\
%& DD  & 0.876 & \textbf{0.878} & 0.877 & 0.181 & \textbf{69.2} & 0.917  \\

\end{tabular} 
\caption{Results on SIGHAN 2005 and 2003 datasets. }\label{tbl:results}
\end{small}
\end{table}

### 2013-07-02 cws/emnlp_cws/introduction.tex
cleaned up results section, added a table to experiment section
writing additions etc

First paragraph talks about why Chinese Word Segmentation is important.

Second paragraph talks about the challenges, specifically ambiguity and unknown words.

Third paragraph: There are two classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, each has their respective advantage and disadvantage: char-based segmenters models the internal structure of word composition better and therefore are more effective at detecting out-of-vocabulary words, however they suffer from inconsistency issues. Word-segmenters are better at memorizing the training word type lexicon, and have better consistency, but not as good at detecting OOV words. An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

Fourth paragraph (maybe consider moving some of this into a related work section and put it at the end): various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.

\cite{Sun:2009:HLT-NAACL} is the most similar in that they also try to directly combine two segmenters -- one char-based and one word-based. But they do it through segmenter bagging, which would require training up 50 or more individual segmenters and poll their results at test time, significantly increases training and testing effort, not practical.
\cite{Sun:2009:HLT-NAACL} presented a latent-variable model. very complicated, hard to train. our method is much simpler and works better than their method.

\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenter based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It's easy to implement and does not require retraining of existing character and word segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model consistently outperform the word and character baselines by significant margin on all 8 datasets. In particular, it improves OOV recall rates and consistency (yet to be validated pending consistency experiment results). It gives the best reported results to date on 6 out of 8 datasets.

>>>>

%First paragraph talks about why Chinese Word Segmentation is important.
Chinese text is written without delimiters between words; as a result, Chinese word segmentation (CWS) is an essential foundational step for many tasks in Chinese natural language processing. As demonstrated by [cite, cite, cite - Pichuan, what else?], the quality and consistency of segmentation has important downstream impacts on system performance in machine translation, [and...].

%Second paragraph talks about the challenges, specifically ambiguity and unknown words.
State-of-the-art performance in CWS is high, with F-scores in the upper 90s. %say this in a nicer way?
Still, challenges remain. Unknown words, also known as out-of-vocabulary (\textsc{oov}) words, lead to difficulties for word- or dictionary-based approaches.
Ambiguity can cause errors when the appropriate segmentation is determined contextually, such as 才能 (``talent") and 才 / 能 (``just able"). % from Gao acl 2003

%Third paragraph: 
There are two primary classes of models: character-based \cite{Xue:2003:IJCLCLP,Tseng:2005:SIGHAN,Zhang:2006:HLT-NAACL,Wang:2010:COLING} and word-based \cite{Andrew:2006:EMNLP,Zhang:2007:ACL}, with corresponding advantages and disadvantages. Character-based segmenters better model the internal compositional structure of words and are therefore more effective at detecting out-of-vocabulary words; however, they suffer from relative inconsistency. % problematic - our experiments show this isn't really true, the CRF is more consistent 6/8 times
Word-based segmenters are better at reproducing the words of the training lexicon and have a higher consistency, but are not as good at detecting \textsc{oov} words. Word-based models have the additional advantage that they tend to capture information from significantly larger contextual spans.
% too detailed?
%Due to the Markov assumption of the linear-chain CRFs that are commonly used in character-based segmentation the models typically only have information about the immediately neighboring characters, while word-based methods tend to capture information from significantly larger contextual spans.

%An additional advantage of word-segmenter is that they can explore larger context than character-based models (this is a little hard to explain without getting into the details of how these models work, maybe leave this piece till later; the basic idea is that character-based models -- i.e., linear-chain CRFs --- have very limited context due to Markov assumption, it typically only have direct information about the immediate neighboring characters, although information from longer-range context does flow because of the sentence-level normalization, its effect is much less direct. Word-based models in contrary directly captures the formation of entire words, say the previous word token has 3 characters, and the current word being considered has 3 characters, then a word-level bigram feature would capture context in neighboring 6 characters.

In this work, we propose a simple and principled joint decoding method for combining character-based and word-based segmenters based on dual decomposition. This method has strong optimality guarantees and works very well empirically. It is easy to implement and does not require retraining of existing character- and word-based segmenters.
Experimental results on standard SIGHAN 2003 and 2005 bake-off evaluations show that our model outperforms the character and word baselines by a significant margin on all 8 datasets. % wait, aren't we showing results for only 7?
In particular, it improves \textsc{oov} recall rates and consistency, % this is now validated
and gives the best reported results to date on 6 out of 7 datasets.

### 2013-07-02 cws/emnlp_cws/relatedwork.tex
writing additions etc

\section{Related Work}
If the Introduction section becomes too long, or we have some space left at the end, we can consider move some of the comparison stuff into this section.

>>>>

\section{Related Work}

\subsection{Character-based Models}
In the most commonly used contemporary approach to character-based segmentation, first proposed by \cite{Xue:2003:IJCLCLP}, CWS is seen as a character sequence tagging task, where each character is tagged on whether it is at the beginning, middle, or end of a word. Conditional random fields (CRFs) are often used for this purpose (cite, cite, cite). In a CRF segmentation model, the probability of a label sequence is given by this equation:

%[add eq here]
% add defs of all the variables

Common linguistic features include character n-grams and morphological suffix/prefix features. Since these features capture information about the compositional properties of characters, they are likely to generalize well to unknown words.

\subsection{Word-based Models}

See \cite{Sun:2010:COLING} for a good description. We used the perceptron based model proposed by \cite{Zhang:2007:ACL}, give the equation of the perceptron, and describe the features. Point out how some of these features basically directly capture the training lexicon.
%
%\subsection{Relative Strength and Weakness}
%Char-based CRF models are better at generalizing over to OOV words (thus higher OOV recall).  (NOTE: 6 out of 8 datasets on test, CRF has better OOV recall, but we should defer to talk about this in the results section). But as a tradeoff, it generates more inconsistent segmentation, and creates lots of spurious words.
% The advantage of Word-based segmenters are that they are more consistent with the training lexicon, words seen in training lexicon are not likely to be segmented into many new ways; disadvantage is that it doesn't generalize well to OOV. Also exact inference is difficult, need to resolve to approximate decoding algorithms such as beam-searching.
%

\subsection{Mixing Models} various mixing approaches have been proposed to combine the merits of these two classes of models \cite{Wang:2006:SIGHAN,Lin:2009:CICLing,Sun:2009:HLT-NAACL,Sun:2010:COLING,Wang:2010:COLING}.

\cite{Sun:2009:HLT-NAACL} is the most similar in that they also try to directly combine two segmenters -- one char-based and one word-based. But they do it through segmenter bagging, which would require training up 50 or more individual segmenters and poll their results at test time, significantly increases training and testing effort, not practical.
\cite{Sun:2009:HLT-NAACL} presented a latent-variable model. very complicated, hard to train. our method is much simpler and works better than their method.

\cite{Lin:2009:CICLing} and \cite{Wang:2006:SIGHAN} both try to incorporate a character-based local classifier model (MaxEnt) with a language model that captures more word-level context.
In order to bring in bigram language model,  \shortcite{Lin:2009:CICLing} gave a heuristic decoding method that involves various conditioning and back-off; \shortcite{Wang:2006:SIGHAN} gave a modified Viterbi algorithm actually has complexity of $O(T^3)$.
